$p$-adic precision

### 2014-02-15 padicprec.tex
todo updated

%\subsection{Ultrametric analysis}
%\label{ssec:ultrametric}

%Similarly to the real case, any finite dimensional normed $K$-vector 
%space is complete and all norms over such a space are equivalent 
%(\emph{i.e.} they define the same topology). Many usual Theorems 
%concerning Banach spaces (\emph{e.g.} open mapping Theorem, closed graph 
%Theorem) remain true in the ultrametric setting.

%\begin{deftn} \label{deftn : diff}
%Let $V, W$ be two normed $K$-vector spaces, let $U \subset V$ be an open 
%subset of $V$ and let $f : U \rightarrow W$ be a map. Then $f$ is called 
%\emph{differentiable} at $v_0 \in U$ if there exists a 
%continuous linear map $f'(v_0) : U \rightarrow W$ such that for any 
%$\varepsilon >0$, there exists an open neighborhood $U_\varepsilon 
%\subset U$ containing $v_0$ with:
%\[ 
%\forall v, w \in U_\varepsilon, \quad
%\Vert f(v)-f(w)-f'(v_0) \cdot \left( v-w \right) \Vert 
%\leq \varepsilon \Vert v-w \Vert. 
%\]
%The linear map $f'(v_0)$ is called the \emph{differential} of $f$ at $v_0$.
%\end{deftn}

%One can derive all usual properties of the differential from this 
%definition: unicity, chain rules, \emph{etc}.

@@

@@

\begin{prop} \label{prop : maj Lambda}
If $m_1$ is a real convex function above $\Lambda((f_n)_{n \geq 1})$.
We define $m_2$ by extending $m_1$ with slope $2$.
Let $r$ be the abscissa of the intersection of $m_2$ and the line defined by $y=-\log \varepsilon+ x.$ Then $e^r$ is enough for \ref{lem:main}.
\end{prop}
\begin{proof}
$r$ is well-defined thanks to corollary \ref{cor : trunc series}, and $m_2 \geq \Lambda((f_n)_{n \geq 2}).$

>>>>

\subsection{Ultrametric analysis}
\label{ssec:ultrametric}

Similarly to the real case, any finite dimensional normed $K$-vector 
space is complete and all norms over such a space are equivalent 
(\emph{i.e.} they define the same topology). Many usual Theorems 
concerning Banach spaces (\emph{e.g.} open mapping Theorem, closed graph 
Theorem) remain true in the ultrametric setting.

\begin{deftn} \label{deftn : diff}
Let $V, W$ be two normed $K$-vector spaces, let $U \subset V$ be an open 
subset of $V$ and let $f : U \rightarrow W$ be a map. Then $f$ is called 
\emph{differentiable} at $v_0 \in U$ if there exists a 
continuous linear map $f'(v_0) : U \rightarrow W$ such that for any 
$\varepsilon >0$, there exists an open neighborhood $U_\varepsilon 
\subset U$ containing $v_0$ with:
\[ 
\forall v, w \in U_\varepsilon, \quad
\Vert f(v)-f(w)-f'(v_0) \cdot \left( v-w \right) \Vert 
\leq \varepsilon \Vert v-w \Vert. 
\]
The linear map $f'(v_0)$ is called the \emph{differential} of $f$ at $v_0$.
\end{deftn}

One can derive all usual properties of the differential from this 
definition: unicity, chain rules, \emph{etc}.

@@

\subsubsection*{Lattices}

@@

\begin{prop} \label{prop : maj Lambda} \label{prop:locanalytic}
If $m_1$ is a real convex function above $\Lambda((f_n)_{n \geq 1})$.
We define $m_2$ by extending $m_1$ with slope $2$.
Let $r$ be the abscissa of the intersection of $m_2$ and the line defined by $y=-\log \varepsilon+ x.$ Then $e^r$ is enough for \ref{lem:main}.
\end{prop}
\begin{proof}
$r$ is well-defined thanks to corollary \ref{cor : trunc series}, and $m_2 \geq \Lambda((f_n)_{n \geq 2}).$
